Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-09-24 paper/tidy-missing-data-paper.Rmd
improving table header

This paper is organized in the following way. Section \@ref(background) provides the background to tidy data principles and tools \@ref(tidy-data-concepts) and missing data representations (\@ref(missing-data-rep-dep)). Section \@ref(existing-software) summarises existing software for handling missing data. The new work extending the tidy tools to facilitate exploring, visualizing, and imputing missing data is discussed in Section \@ref(extensions). Graphics (\@ref(graphics)) and Numerical summaries (\@ref(num-sum)) of missing values are then discussed. An application illustrating the use of the new methods is shown in Section \@ref(case-study). Section \@ref(discussion) discusses strengths, limitations, and future directions.

@@

### The tidyverse {#the-tidyverse}

@@

table_of_fun <- tibble::tibble(
  "Missing Function" = c("n_miss", 
                         "prop_miss", 
                         "pct_miss",
                         "pct_miss_case",
                         "pct_miss_var"),
  "missing value" = c(n_miss(airquality),
                      prop_miss(airquality),
                      pct_miss(airquality),
                      pct_miss_case(airquality),
                      pct_miss_var(airquality)),
  "Complete function" = c("n_complete",
                          "prop_complete",
                          "pct_complete",
                          "prop_complete_case",
                          "pct_complete_var"),
  "complete value" = c(n_complete(airquality), 
                       prop_complete(airquality), 
                       pct_complete(airquality),
                       pct_complete_case(airquality), 
                       pct_complete_var(airquality))
) %>%
  mutate_if(is.numeric,round,2)

>>>>

This paper is organized in the following way. Section \@ref(background) provides the background to tidy data principles and tools (\@ref(tidy-data-concepts)) and missing data representations (\@ref(missing-data-rep-dep)). Section \@ref(existing-software) summarises existing software for handling missing data. The new work extending the tidy tools to facilitate exploring, visualizing, and imputing missing data is discussed in Section \@ref(extensions). Graphics (\@ref(graphics)) and Numerical summaries (\@ref(num-sum)) of missing values are then discussed. An application illustrating the use of the new methods is shown in Section \@ref(case-study). Section \@ref(discussion) discusses strengths, limitations, and future directions.

@@

### Tidy data and tidy tools {#the-tidyverse}

@@

table_of_fun <- tibble::tibble(
  "Missing function" = c("n_miss", 
                         "prop_miss", 
                         "pct_miss",
                         "pct_miss_case",
                         "pct_miss_var"),
  "Missing value" = c(n_miss(airquality),
                      prop_miss(airquality),
                      pct_miss(airquality),
                      pct_miss_case(airquality),
                      pct_miss_var(airquality)),
  "Complete function" = c("n_complete",
                          "prop_complete",
                          "pct_complete",
                          "prop_complete_case",
                          "pct_complete_var"),
  "Complete value" = c(n_complete(airquality), 
                       prop_complete(airquality), 
                       pct_complete(airquality),
                       pct_complete_case(airquality), 
                       pct_complete_var(airquality))
) %>%
  mutate_if(is.numeric,round,2)
